Random_Effects

### 2023-08-15 Code/GLMM.Rmd
added some stuff to be able to view summary statistics

```{r}
summary(men_pooled_year_gamma_log)

@@

@@

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model
```{r}
#7
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.1)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.1)
```
```{r}
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.08)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.08)
```

>>>>

```{r}
summary(men_pooled_year_gamma_log)
summary(men_old_pooled_year_gamma_log)
```

@@

```{r}
summary(men_pooled_batch_gamma_log)
```

@@

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model
```{r}
#7
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.1)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.1)
```

```{r}
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.09)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.09)
```

```{r}
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.08)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.08)
```
